Age-related changes in plant growth and traits

### 2015-10-15 Flowering_parts_charts.Rmd
adding estimates of nectar production to reproduction data

``` {r}
accessoryList <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")
accessoryListShort <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShort.csv")
accessoryListShortest <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShortest.csv")

col.barplot <- function(x=NULL){
  ret <- c("cyan4","cyan1","darkslategray3","firebrick","firebrick1","firebrick2","firebrick3","gold","bisque","chartreuse2","chartreuse3","chartreuse4","chartreuse2","deepskyblue",
           "dodgerblue2","deepskyblue","deepskyblue4","darkorange","darkorange1","darkorange2","darkorange3","darkorange4","darkorange3")
  names(ret) <- c("seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature",
                  "bract","pedicel","green_parts","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")

@@

@@

SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
SummaryInvest$prop_weight <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
SummaryInvest$labels <- paste(SummaryInvest$parts_fewer," (",SummaryInvest$prop_weight,")")
SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer,levels=c(c("seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted",
                                                                                 "bract","pedicel","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green")))),]
```

@@

SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
SummaryInvest$prop_weight_spp <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
SummaryInvest$labels <- paste(SummaryInvest$parts_fewer_yet," (",SummaryInvest$prop_weight,")")
SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer_yet,levels=c(c("bud","petals","calyx","finished_flower","fruit_seed_immature","seed","seed_pod","fruit_mature","bract","pedicel","inflorescence_stalk","green_parts","cone")))),]
```

@@

View(SummaryInvestParts)

@@

```{r}
barplot_data <- select(SummaryInvest,species, parts_fewer_yet, prop_weight)
barplot_data <- spread(barplot_data,species,prop_weight,fill=0,drop=FALSE)
barplot_data <- barplot_data[order(factor(barplot_data$parts_fewer_yet,levels=c(c(
  "bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature","seed","seed_pod","fruit_mature",
  "bract","pedicel","inflorescence_stalk","green_parts","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")))),]

@@

#pdf("figs2/Flower_parts_barchart.pdf", height=8, width=11)
#plot
barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.8,cex.names=.8,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1.2,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))
#dev.off()
##For pie charts

data <- subset(SummaryInvest,weight>0)
data <- split(data, data$species)

>>>>

Always run
Opening files

``` {r}
accessoryList <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")
accessoryListShort <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShort.csv")
accessoryListShortest <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShortest.csv")
tissue_energy <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/tissue_energy.csv")
nectar <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nectar.csv")

col.barplot <- function(x=NULL){
  ret <- c("black","cyan4","cyan1","darkslategray3","firebrick","firebrick1","firebrick2","firebrick3","gold","bisque","chartreuse2","chartreuse3","chartreuse4","chartreuse2","deepskyblue",
           "dodgerblue2","deepskyblue","deepskyblue4","darkorange","darkorange1","darkorange2","darkorange3","darkorange4","darkorange3")
  names(ret) <- c("nectar","seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature","bract","pedicel","green_parts","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")

@@

Always run 
process nectar
```{r}
Invest_nectar <-subset(Invest2,(species=="BAER"|species=="GRBU"|species=="GRSP"|species=="HATE")&part=="flower_stigma")
Invest_nectar$part ="nectar"
Invest_nectar$parts_fewer ="nectar"
Invest_nectar$parts_fewer_yet ="nectar"
Invest_nectar$weight = 0

SummaryNectar <- 
  Invest_nectar %>%
  group_by(parts_fewer_yet,species) %>%
  summarise_each(funs(sum),count)

SummaryNectar<- merge(SummaryNectar,nectar, by=c("species"),all.x=TRUE)
SummaryNectar$tissue_energy <- SummaryNectar$count*SummaryNectar$days*SummaryNectar$energy_daily/1000
SummaryNectar <- select(SummaryNectar,-count,-days,-energy_daily, -part)
SummaryNectar$accessory_part = "nectar"
```

@@

SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
SummaryInvest$prop_weight <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
SummaryInvest$labels <- paste(SummaryInvest$parts_fewer," (",SummaryInvest$prop_weight,")")
SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer,levels=c(c("seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted",
                                                                                 "bract","pedicel","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green")))),]
```
View(SummaryInvest)

@@

SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
SummaryInvest$prop_weight <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)

SummaryInvest <- merge(SummaryInvest,tissue_energy,by=c("parts_fewer_yet"),all.x=TRUE)
SummaryInvest$tissue_energy <- SummaryInvest$weight*SummaryInvest$energy/1000

SummaryInvest <- bind_rows(SummaryInvest,SummaryNectar)

SummaryEnergySpp <- 
  SummaryInvest %>%
  group_by(species) %>%
  summarise_each(funs(sum),tissue_energy)

names(SummaryEnergySpp) <- c("species","energy_spp")
SummaryInvest <- merge(SummaryInvest,SummaryEnergySpp,by=c("species"),all.x=TRUE)
SummaryInvest$prop_energy <- round(SummaryInvest$tissue_energy / SummaryInvest$energy_spp,digits=3)

SummaryInvest$labels <- paste(SummaryInvest$parts_fewer_yet," (",SummaryInvest$prop_weight,")")
SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer_yet,levels=c(c("nectar","bud","petals","calyx","finished_flower","fruit_seed_immature","seed","seed_pod","fruit_mature","bract","pedicel","inflorescence_stalk","green_parts","cone")))),]
```

View(SummaryInvest)
View(Invest2)

@@

unique(SummaryInvestParts$parts_fewer)

@@

#barplot by dry weight
```{r}
barplot_data <- select(SummaryInvest,species, parts_fewer_yet, prop_weight)
barplot_data <- spread(barplot_data,species,prop_weight,fill=0,drop=FALSE)
barplot_data <- barplot_data[order(factor(barplot_data$parts_fewer_yet,levels=c(c(
  "bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature","seed","seed_pod","fruit_mature",
  "bract","pedicel","inflorescence_stalk","green_parts","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")))),]

@@

#pdf("figs2/Flower_parts_barchart.pdf", height=8, width=11)
#plot
#win.metafile("figs2/RA_talk_barplot.wmf", height=4, width=10)
#plot
par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))

#dev.off()
```

#barchart by kJ
```{r}
barplot_data <- select(SummaryInvest,species, parts_fewer_yet, prop_energy)
barplot_data <- spread(barplot_data,species,prop_energy,fill=0,drop=FALSE)
barplot_data <- barplot_data[order(factor(barplot_data$parts_fewer_yet,levels=c(c("nectar",
  "bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature","seed","seed_pod","fruit_mature",
  "bract","pedicel","inflorescence_stalk","green_parts","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")))),]

pdf("figs2/Flower_parts_barchart_energy.pdf", height=8, width=11)

#win.metafile("figs2/RA_talk_barplot_energy.wmf", height=4, width=10)
plot
par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))

dev.off()
```

##For pie charts
```{r}
data <- subset(SummaryInvest,weight>0)
data <- split(data, data$species)
